The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-14 methods/ms.tex
mostly paper mods?

This paper details the survey observations and methods.  We treat
carefully the determination of pointing and flux calibration errors
and compare our results to the literature.  Data processing algorithms
that separate astronomical signals from time-variable atmospheric flux
in the data time-stream are discussed.  The algorithms reproduce the
structure of the astronomical sky on a limited range of angular scales
and produce artifacts in the vicinity of bright sources. Specifically,
extended emission smooth on scales larger than about 5\arcmin\ is not
fully recovered in the images.  The spatial frequency response
function of the Bolocam Galactic Plane Survey is discussed.

@@

\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright
molecular emission lines are shown at their rest frequencies.  Note
that the Bolocam passband rejects $>90\%$ of the $^{12}$CO flux,
leaving our continuum measurements largely uncontaminated.  SO and
CH$_3$OH lines are probably the dominant contributors to line flux in
the passband.  \citet{nummelin1998} found that 22\% of the flux in one
pointing towards Sgr B2 was from lines, and \citet{yoshida2005}
reported $>40\%$ in Orion A from line emission. \TBD\ Other lines
lying in the Bolocam passband include CS($5\to4$) and ($6\to5$) (245
and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267 GHz).}
{fig:Bandpass}{1.0}

>>>>

This paper details the survey observations and methods.  We treat
carefully the determination of pointing and flux density calibration errors
and compare our results to the literature.  Data processing algorithms
that separate astronomical signals from time-variable atmospheric flux density
in the data time-stream are discussed.  The algorithms reproduce the
structure of the astronomical sky on a limited range of angular scales
and produce artifacts in the vicinity of bright sources. Specifically,
extended emission smooth on scales larger than about 5\arcmin\ is not
fully recovered in the images.  The spatial frequency response
function of the Bolocam Galactic Plane Survey is discussed.

@@

\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright
molecular emission lines are shown at their rest frequencies.  Note
that the Bolocam passband rejects $>90\%$ of the $^{12}$CO flux,
leaving our continuum measurements largely uncontaminated.  SO and
CH$_3$OH lines are probably the dominant contributors to line flux in
the passband.  \citet{nummelin1998} found that 22\% of the flux in one
pointing towards Sgr B2 was from lines, and \citet{yoshida2005}
reported $>40\%$ in Orion A from line emission over the 260-328 GHz band. \TBD\ Other lines
lying in the Bolocam passband include CS($5\to4$) and ($6\to5$) (245
and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267 GHz).}
{fig:Bandpass}{1.0}
